Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-07 tex/ms.tex
add some discussion text, fleshing out broadening text

BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
by convolution with a Gaussian in wavelength space (to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by $\sigma$.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes 
the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:calibrated_spectrum} we also show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:calibrated_triangle} we show the
marginalized and joint PDFs for the parameters.

@@

\begin{figure}[h!]
\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
  the posterior for the model, and residuals}
\end{figure}

\begin{figure}[h!]
\caption{Show the observed photometric SED and draws from the
  posterior, for one cluster.}
\end{figure}

\begin{figure}[h!]
\caption{Show a corner plot of selected relevant parameters, for one cluster.}
\end{figure}

\begin{figure}[h!]
\caption{Money plot.  Show the difference between the parameters
  inferred from the calibrated and uncalibrated spectra, for each cluster.}
\end{figure}

@@

BDJ INSERT WORDS HERE.
BDJ random issues, collected here in case we want to address them and
to keep me from cluttering up the main text: effective aperture
corrections (i.e. we're implicitly assuming photometry and
spectroscopy sample the same population).  Sky subtraction residuals.
Model resolution and instrument resolution.  Method only useful when
you have a model for the mean spectrum?  How to interpret GP
residuals, as a fn of S/N?  Photometric upper limits? Infer the
wavelength solution as well - stellar population (and telluric lines)
as your arc. Combinations of broadening in velocity space (physical)
and in wavelength space (instrumental)

>>>>

BDJ IMPROVE DISCUSSION OF BROADENING.  The model spectra are smoothed
by convolution with a Gaussian in wavelength space (to model the MMT
line-spread function) and are interpolated to the wavelength points of
the of the observed spectrum while taking into account the
redshift. The instrumental resolution is given by $\sigma$.  Discuss
Intrinsic resolution of model spectra (MILES), whether instrumentasl
resolution is larger, smaller, or comparable to intrinsic velocity
broadening.

@@

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G_\sigma$ represents a Gaussian of unit area 
and standard deviation $\sigma$, 
$\otimes$ indicates convolution, 
and the full parameter set $\theta$ now includes
the instrumental wavelength broadening $\sigma$, 
and the dispersion $\sigma_e$ and
amplitudes $A_\ell$ of the $N_l$ nebular and interstellar emission
lines.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:inferred_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:inferred_spectrum} we also show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:inferred_params} we show the
marginalized and joint PDFs for the parameters.

@@

\begin{figure}[h!]
\caption{Show, for one cluster, the (un)calibrated spectral data, draws from
  the posterior for the model, and residuals \label{fig:inferred_spectrum}}
\end{figure}

\begin{figure}[h!]
\caption{Show the observed photometric SED and draws from the
  posterior, for one cluster.\label{fig:inferred_sed}}
\end{figure}

\begin{figure}[h!]
\caption{Show a corner plot of selected relevant parameters, for one
cluster. \label{fig:inferred_params}}
\end{figure}

\begin{figure}[h!]
\caption{Money plot.  Show the difference between the parameters
  inferred from the calibrated and uncalibrated spectra, for each
  cluster.\label{fig:boom}}
\end{figure}

@@

BDJ INSERT WORDS HERE.  We have shown that we can combine photometric
and spectroscopic data in a principled way to infer physical
properties.  We do not resort to an arbitrary down-weighting or
up-weighting of certain data. Instead, we explicitly model our
uncertainty in the spectral calibration.  This combination of
spectroscopy and photometry reduces the need for spectrophotometric
calibration for a number of applications.  Furthermore, our strategy
easily extensible to more complicated models, which include for
example night sky line emission in the spectroscopy, wavelength
calibration.

BDJ misc issues, collected here in case we want to address them and
to keep me from cluttering up the main text: effective aperture
corrections (i.e. we're implicitly assuming photometry and
spectroscopy sample the same population).  Sky subtraction residuals.
Model resolution and instrument resolution.  Method only useful when
you have a model for the mean spectrum?  How to interpret GP
residuals, as a fn of S/N?  Photometric upper limits? Infer the
wavelength solution as well - stellar population (and telluric lines)
as your arc. Combinations of broadening in velocity space (physical)
and in wavelength space (instrumental)
